A Standardized Effect Size for Evaluating and Comparing the Strength of Phylogenetic Signal

### 2020-07-17 Manuscript/PNAS-Adams-01.Rmd
fig mucking

# Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
author:
  - name: Dean C. Adams
    affiliation: a,1
  - name: Erica K. Baken
    affiliation: a,b
  - name: Michael L. Collyer
    affiliation: b
address:
  - code: a
    address: Department of Ecology, Evolution, and Organismal Biology, Iowa State University, Ames, Iowa, 50010. USA.
  - code: b
    address: Department of Science, Chatham University, Pittsburgh, Pennsylvania, 15232. USA.

corresponding_author:
  - code: 1
    text: "To whom correspondence should be addressed. E-mail: dcadams@iastate.edu"

@@

  ^1^To whom correspondence should be addressed. E-mail: dcadams@iastate.edu

@@

![Response of effect sizes $Z_\lambda$ and $Z_\kappa$ to increasing strength of Brownian motion.<span data-label="fig:f3"></span>](new.fig.3.temp.png)

>>>>

# Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
author:
  - name: Dean C. Adams
    affiliation: a,2
  - name: Erica K. Baken
    affiliation: a,b
  - name: Michael L. Collyer
    affiliation: b
address:
  - code: a
    address: Department of Ecology, Evolution, and Organismal Biology, Iowa State University, Ames, Iowa, 50010. USA.
  - code: b
    address: Department of Science, Chatham University, Pittsburgh, Pennsylvania, 15232. USA.

corresponding_author:
  - code: 2
    text: "To whom correspondence should be addressed. E-mail: dcadams@iastate.edu"

@@

  ^2^To whom correspondence should be addressed. E-mail: dcadams\@iastate.edu

@@

![Response of effect sizes $Z_{\lambda}$ and $Z_{\kappa}$ to increasing strength of Brownian motion.<span data-label="fig:f3"></span>](new.fig.3.temp.png)
